---
title: "311 Park Data"
author: "Nicole LaPointe Jameson"
date: "February 12, 2016"
output: html_document
---

#Importing Relevant 311 Data

##Establishing the Workbench
```{r, message=FALSE}
library(data.table)
```

##Importing and Renaming the Data

```{r, message=FALSE}
info <- fread("/Users/NMLJ/Downloads/2013_311_Service_Requests.csv", select=c("Agency Name","Complaint Type","Location Type", "City", "Facility Type", "Latitude", "Longitude"))

info$Agency <- as.factor(info$`Agency Name`)

info$Complaint <- as.factor(info$`Complaint Type`)

info$Location <- as.factor(info$`Location Type`)

info$City <- as.character(info$City)

info$Facility <- as.factor(info$`Facility Type`)

info$Lat <- info$Latitude
info$Lon <- info$Longitude
```

Using Excel Filters, I then manually deleted redunant and unnessesary columns

##Filtering and Cleaning
```{r, message=FALSE}
NYCinfo <- read.csv("/Users/NMLJ/Desktop/GitHub/project2-group10/data/infoFiltered.csv", header=TRUE, skipNul = TRUE)

#NA's Removed
NYCinfo <- na.exclude(NYCinfo)
```

## The Final Data Set

This set only includes complaints within Public Parks or Playgrounds, and is factored by type of complaint: Animals in the park, homeless encampment, need for maintenance or facilities, and noise, all which could affect your bathroom-going experience.

```{r}
ParkProb <- fread("/Users/NMLJ/Desktop/GitHub/project2-group10/data/infoFiltered.csv", select = c("Complaint", "Lat","Lon"))

ParkProb$Complaint <- as.factor(ParkProb$Complaint)

ParkProb <- na.exclude(ParkProb)

write.csv(x=ParkProb, file="/Users/NMLJ/Desktop/GitHub/project2-group10/data/ParkProb.csv")
```

