---
title: "Idea’s on the data analysis"
author: "Ao Liu"
date: "February 18, 2016"
output: pdf_document
---

###What we want to do
1.  Compare the restroom density and the number of restroom evry person have in terms of borough, population, even the community district(depends on whether we can get the zip code of every cd)
2.  figure out the correlation between public restroom and some other public factors
3.  suggestion on building some more restrooms in certain area based on our own knowledge

####The distribution of the restrooms:

```{r}
insert map here
```
But this is just the total number of the toilets in different districts, which fails to consider the size of each district. so we calculate the number of restrooms in every square meter, and draw another plot:

```{r}
insert map here
```

here we can see that XXX places has the most restrooms, whereas ... has less room in every unit area.


####How many public restroom does everyone own?
However, more restrooms in every unit area doesn't guarantee people can use the restroom at ease. For those of the place which has tourists attractions, the poplulation is higher, so the demand of the restrooms is higher too, thus it makes more sense fot us to compare the number of restrooms in every square meter per person:

```{r}
insert map here
```


This time, we can see clearly: people in XXX place has the least pressure in finding the toilet, whereas people in xxx place have the most problem in finding their restrooms.

So now we try to figure out a resonable explaination of the distribution above.
Here we choose some factors that interest us: population of every borough, GDP of every borough.


We draw a scatterplot matrix at first, and then get rid of the factors that doesn't show strong coorelation with the density of the toilet.



To sum up, we find a genral pattern for the distribution of the public restrooms in NYC, which means most of the places that follow this pattern could satisfy the need for people finding the restroom. 

It is worthy to pay attention to the putliers of this plot, which doesn't fit well to the pattern, so for xxx place, this place has a very low onwership of the restroom per person, we might suggest the local government to build more toilet in this area.

Above is our analysis of the restroom data, since we have already known well about the its relationship with many other factors, we might want to take advantage of it. Thus, we created a recommendation system for people outdoors in NYC, by inputing some key factors we have mentioned above, we can help the user to go to a satisfying restroom as soon as possible.

We even give it a name:...

Here's what it looks like:



